### 2021-03-12 paper_1.tex
End paper1

\subsection{INTRODUCTION}
In order to reduce the complexity in the analysis of a scene, a useful method 
is introduced to detect potential information, such as regions or 
objects, simultaneously. This method is called "\emph{Visual Saliency}". Before introducing
the topic, four types of concepts must be explained: (1)\emph{Fixations}: 
they concern the scene framed by the human eye. They are used to compare 
the methods of forecasting fixations. (2)\emph{ROI}: each region contains information, 
such as light or dark objects, which is intended to be separated.(3)\emph{Salient objects}: 
animals, people, cars etc. (4)\emph{Salient edges}: boundary of each object. The proposed 
method is based on carrying out a \emph{Salient Structure (SS) Detection},
useful for identifying the four previous properties, both in cluttered and 
simple scenes. The proposed framework is called \emph{CGVS (contour-guided visual 
search)}. This visual search tool identifies the targets using two types of 
paths: (1)\emph{selective path}: the boundaries of each object are detected, useful 
for estimating the position and size of the ROI: (2)\emph{non-selective path}: it 
can be properties such as color, luminary, texture etc. This search strategy 
carries out parallel processing on both paths, extracting global and local 
information. Finally, a Bayesian inference is applied to integrate the contour 
based spatial prior (CBSP), a useful method for extracting information on 
the boundaries, and local information in order to identify the salience of each 
pixel.

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper1/selective and non-selective pathways.png}
    \centering
    \caption{The flowchart of the porposed system}
    \label{fid: flowchart}
\end{figure}

@@

\subsubsection{\emph{Contour-Based Spatial Prior (CBSP)}}
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper1/CBSP.png}
    \centering
    \caption{CBSP reconstruction.}
    \label{fid: CBSP}
\end{figure}
Within the non-selective path, the crucial operation is to calculate the 
approximate spatial weights of salience based on the distribution of the previously 
detected contours. In this path there is the problem of determining 
the local information of each object. The solution to the problem is based 
on an operation that fills the regions delimited by these contours. A very 
efficient method proposed in \cite{0747815500} result is used for the extraction of the contours.
An example of CBSP reconstruction is shown in Fig. \ref{fid: CBSP}. Each pixel 
has a direction represented by a radius $ d_r $ which is equal to $d_r = min (H, W) / 3$, where 
\emph{H} and \emph{W} correspondingly indicate the width and height of the entire image.
The diameter divides the circle into two parts where, on each of these, for 
each pixel belonging to the edge, the average response of the edge (AER) will 
be calculated. This calculation is useful in deciding which of the two halves 
will belong to the salient region. Each spatial weight of salience is denoted 
by $ S_e $, while the added bias is denoted by $ S_c $ and both are normalized in the 
range of [0,1]. The value, which in turn will be normalized, of CBSP is given by: $$ S_w = S_e + S_c $$

\subsubsection{Low-Level Feature Extraction}
Features such as color (rgb), luminance (flum) and texture are extracted in 
parallel. There are complicated regions in a texture that can be represented. 
For this purpose, the texture channel ($ {f_{ed}} $)  has been introduced, which is 
useful to better represent the salient regions using the contour density (ED). 
The texture channel is calculated by using an 11x11 filter that smooths the 
edges.

\subsubsection{Bayesian Inference With Contour Guidance}
Bayesian inference gives the possibility to calculate the probability that a 
pixel x may belong to a salient structure s. This probability is computed as:
$$ p(s|x) = \frac{p(s)p(x|s)}{p(s)p(x|s)+p(b)p(x|b) } $$
Where $ p(x|s) $ is the probability of a pixel belonging to a salient structure, 
$ p(x|b) $ is the probability that a pixel belongs to the background, $ p(b)=1-p(s) $,
finally $ p(s)=Sw $ represents the CBSP value. The implementation 
details are as follows.
\begin{enumerate}
    \item \emph{Predict the size of Potential Structure}: this procedure, through a binarization of the map obtained 
    from $ p(s) $, separates the salient structures from the background, all 
    through the use of a threshold. This threshold is calculated using the 
    local parameters (color, luminance, etc.), a percentage not greater than 
    50\% useful to denote the size of the salient structure, an initial weight 
    and finally two sets of pixels corresponding to the background and the 
    foreground (salient structure).
    \item \emph{Evaluate the Importance of Each Feature}: a feature is considered important 
    when the difference between the average pixel values of its 
    salient structure and those of the background is large enough, i.e. when \emph{$ w_i $} 
    takes on a satisfiable value.
    \item \emph{Calculate the Observation Likelihood}:in order to calculate the observed 
    probabilities, the different color channels \emph{($ f_{lum}, f_{rg}, f_{by}, f_{ed} $)} are used, 
    and the distribution functions $ p(x_i | S_{T_{opt}}) $ and $ p(x_i | B_{T_{opt}}) $ where $ S_{T_{opt}} $ 
    represents the set of pixels belonging to the structure salient, while 
    $ B_{T_{opt}} $ represents the set of pixels belonging to the background.
    $$ p(x|s) = \prod_{i \in {\{} f_{lum}, f_{rg}, f_{by}, f_{ed} {\}}} {(p(x_i | S_{T_{opt}}))^{w_i}} $$
    $$ p(x|b) = \prod_{i \in {\{} f_{lum}, f_{rg}, f_{by}, f_{ed} {\}}} {(p(x_i | B_{T_{opt}}))^{w_i}} $$
    \item \emph{Enhance the Salient Structure by Iterating}: the salient structures, at 
    each instant \emph{t}, with $ t = t_0,…, t_n $, are iteratively improved by applying 
    a median filter on each of them. In addition, the weight attributed to 
    the importance of each feature is changed. Finally, the CGVS model 
    will operate on a set of instants \emph{t}, thus forming the contour-guided 
    visual search.
\end{enumerate}

@@

\subsubsection{\emph{Basic Property of the Proposed Model}}
The proposed system allows to carry out a multiple search of objects. In 
comparison to the work of Itti et al. \cite{0747815505} the proposed system is able to detect, 
after several iterations, the region and therefore the salient object.

\subsubsection{\emph{Fixation Prediction}}
The prediction of fixation indicates the likelihood with which a human is 
looking at a given position in the scene. There are several metrics that are 
used to evaluate the prediction such as Natural Scanpath Saliency (NSS) 
and ROC (AUC). In the following article the ROC method is mainly used, 
on three types of datasets, to compare the proposed system with o already 
existing at the state of the art, as shown in Fig. \ref{fig: ROC}.
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper1/ROC.png}
    \centering
    \caption{ROC comparison.}
    \label{fig: ROC}
\end{figure}

@@

\subsubsection{\emph{Salient Object Detection}}
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper1/metrics.png}
    \centering
    \caption{Metrics comparison.}
    \label{fig: metrics}
\end{figure}
To compare the performance of the salient object detection, metrics such 
as Precision, Recall, F-score, Weighted F-score and MAE (Mean Absolute 
Error) were used on three types of datasets (ASD, ECSSD, PASCALS). The 
results showed that for the first two metrics (P-R), systems such as HS and 
RF are the best, while for the F-score the proposed method is able to consider 
a greater range of thresholds. As it can be seen, in these two metrics the 
proposed system (\emph{CGVS($ t_2 $)}) considers the central bias unlike the others. 
If the central bias were not considered, the results decrease but are still 
satisfactory (\emph{CGVS''}). However, in the remaining two metrics, the proposed 
system is the best, except in the PASCALS dataset where the best is the RF 
method.

\subsubsection{\emph{Between Saliency Map and Salient Object}}
Most fixation prediction methods perform poorly when used to detect salient 
objects. To solve this problem, a two-dimensional Gaussian distribution is 
applied to each salience map derived from any method. The derived output 
will be used as an initial CBSP from which the salient objects can be 
extracted with the previously proposed calculations. The metrics, used to 
measure the performance of the different methods, improve if the methods 
replace their salience map with CBSP.

\subsubsection{\emph{Extended Saliency-Related Applications}}
The peculiarity of the proposed method also lies in the search for salient 
edges. This process is possible by replacing the four color components with 
three luminance gradients and two color-opponent channels. The system also 
proves to be capable of being able to detect text as well.

@@

\subsection{DISCUSSION}
The proposed model searches for salient structures and associated objects 
without using tools, such as the superpixel technique, adopted by other methods. 
The system can be extended by introducing other local features such as 
(e.g., depth, motion, etc.) to be used also in video processing. It is possible 
to carry out an analysis of the scene using unsupervised learning methods. 
Finally, this method offers a dual use. In a cluttered scene with no dominant 
objects, the system will function as a fixation prediction model. On the other 
hand, with simple scenes, the system reveals the existing dominant objects.

>>>>

\subsection{INTRODUCTION}
In order to reduce the complexity in the analysis of a scene, a useful method 
is introduced to detect potential information, such as regions or 
objects, simultaneously. This method is called "\emph{Visual Saliency}". Before introducing
the topic, four types of concepts must be explained: (1)\emph{Fixations}: 
they concern the scene framed by the human eye (ground-truth), used to benchmark 
fixation prediction methods. (2)\emph{ROI}: each region contains information, such 
as light or dark objects, which is intended to be separated.(3)\emph{Salient objects}: 
animals, people, cars etc. (4)\emph{Salient edges}: boundary of each object. The proposed 
method is based on carrying out a \emph{Salient Structure (SS) Detection},
useful for identifying the four previous properties, both in cluttered and 
simple scenes. The proposed framework is called \emph{CGVS (contour-guided visual 
search)}. This visual search tool identifies the targets using two types of 
pathsways: (1)\emph{selective pathway}: the boundaries of each object are detected, useful 
for estimating the position and size of the ROI: (2)\emph{non-selective pathway}: it 
can be properties such as color, luminary, texture etc. This search strategy 
carries out parallel processing on both paths, extracting global and local 
information. Finally, a Bayesian inference is applied to integrate the contour 
based spatial prior (CBSP), and local information in order to identify 
the salience of each pixel.

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper1/selective and non-selective pathways.png}
    \centering
    \caption{The flowchart of the porposed system.}
    \label{fid: flowchart}
\end{figure}

@@

\subsubsection{\emph{Contour-Based Spatial Prior (CBSP)}}
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper1/CBSP.png}
    \centering
    \caption{CBSP reconstruction.}
    \label{fid: CBSP}
\end{figure}
Within the non-selective path, the crucial operation is to calculate the 
approximate spatial weights of salience based on the distribution of the previously 
detected contours. In this path there is the problem of determining 
the local information of each object. The solution to the problem is based 
on an operation that fills the regions delimited by these contours \cite{0747815567}. A very 
efficient method proposed in \cite{0747815570} result is used for the extraction of the contours.
An example of CBSP reconstruction is shown in Fig. \ref{fid: CBSP}. Each pixel 
has a direction represented by a radius $ d_r $ which is equal to $d_r = min (H, W) / 3$, where 
\emph{H} and \emph{W} correspondingly indicate the width and height of the entire image.
The diameter divides the circle into two parts where, on each of these, for 
each pixel belonging to the edge, the average response of the edge (AER) will 
be calculated. This calculation is useful in deciding which of the two halves 
will belong to the salient region. Each spatial weight of salience is denoted 
by $ S_e $, while the added center-bias, which is modeled by a Gussian 
mask having standard deviation as $ \sigma_c = min (H, W) / 3 $, is denoted by $ S_c $ and 
both are normalized in the range of [0,1]. The value, which in turn will be 
normalized, of CBSP is given by: $$ S_w = S_e + S_c $$

\subsubsection{Low-Level Feature Extraction}
In the selective path, features such as complementary colors ($ f_{rg} = r-g$, 
$ f_{by} = b-(r+g)/2 $), luminance ($ f_{lum} = (r+g+b)/3 $) and texture are 
extracted. In addition, the density of the edges ($ f_{ed} $) is extracted, useful to 
represent the level of density of the edges, smoothed by a median filter of 
11x11 pixels.

\subsubsection{Bayesian Inference With Contour Guidance}
Bayesian inference gives the possibility to calculate the probability that a 
pixel \emph{x} may belong to a salient structure \emph{s}. This probability is computed as:
$$ p(s|x) = \frac{p(s)p(x|s)}{p(s)p(x|s)+p(b)p(x|b) } $$
Where $ p(x|s) $ is the probability of a pixel belonging to a salient structure, 
$ p(x|b) $ is the probability that a pixel belongs to the background, $ p(b)=1-p(s) $,
finally $ p(s)=Sw $ represents the CBSP value. The implementation 
details are as follows.
\begin{enumerate}
    \item \emph{Predict the size of Potential Structure}: this procedure, through a binarization 
    of the map obtained from $ p(s) $, separates the salient structures 
    from the background, all through the use of a threshold. This 
    threshold is calculated using local parameters (color, luminance, etc.), 
    a threshold $ T_k $ no greater than 50\% of the size of the entire image, useful 
    for denoting the size of the salient structure, an initial non-zero 
    weight and finally two sets of pixels ($ B_{T_k}$ , $ S_{T_k}$) corresponding to the background 
    and foreground (salient structure).
    \item \emph{Evaluate the Importance of Each Feature}: a feature is considered important 
    when the difference between the average pixel values of its 
    salient structure and those of the background is large enough, i.e. when $ w_i $ 
    takes on a satisfiable value.
    \item \emph{Calculate the Observation Likelihood}:in order to calculate the observed 
    probabilities, the different color channels \emph{($ f_{lum}, f_{rg}, f_{by}, f_{ed} $)} are used, 
    and the distribution functions $ p(x_i | S_{T_{opt}}) $ and $ p(x_i | B_{T_{opt}}) $ where $ S_{T_{opt}} $ 
    represents the set of pixels belonging to the structure salient, while 
    $ B_{T_{opt}} $ represents the set of pixels belonging to the background.
    $$ p(x|s) = \prod_{i \in {\{} f_{lum}, f_{rg}, f_{by}, f_{ed} {\}}} {(p(x_i | S_{T_{opt}}))^{w_i}} $$
    $$ p(x|b) = \prod_{i \in {\{} f_{lum}, f_{rg}, f_{by}, f_{ed} {\}}} {(p(x_i | B_{T_{opt}}))^{w_i}} $$
    \item \emph{Enhance the Salient Structure by Iterating}: the salient structures, at 
    each instant \emph{t}, with $ t = t_0,…, t_n $, are iteratively improved by applying 
    a median filter on each of them. In addition, the weight attributed to 
    the importance of each feature is changed. Finally, the CGVS model 
    will operate on a set of instants \emph{t}, thus forming the contour-guided 
    visual search.
\end{enumerate}

@@

\subsubsection{\emph{Basic Property of the Proposed Model}}
In comparison to the work of Itti et al. \cite{0747815505} the proposed system is able to:
\begin{enumerate}
    \item Automatically select the size of potential salient structures and assign them a weight;
    \item Detect multiple objects in a scene;
    \item Include an iterative process that improves research;
\end{enumerate}

\subsubsection{\emph{Fixation Prediction}}
The fixation prediction indicates the likelihood with which a human is 
looking at a given position in the scene. There are several metrics that are 
used to evaluate the prediction such as Natural Scanpath Saliency (NSS) 
and ROC (AUC). In the following article the ROC method is mainly used, 
on three types of datasets, to compare the proposed system with others already 
existing at the state of the art, as shown in Fig. \ref{fig: ROC}.
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper1/ROC.png}
    \centering
    \caption{ROC comparison.}
    \label{fig: ROC}
\end{figure}

@@

\subsubsection{\emph{Salient Object Detection}}
To compare the performance of the salient object detection, metrics such 
as Precision, Recall, F-score, Weighted F-score and MAE (Mean Absolute 
Error) were used on three types of datasets (ASD, ECSSD, PASCALS). The 
results showed that for the first two metrics (P-R), systems such as HS and 
RF are the best, while for the F-score the proposed method is able to consider 
a greater range of thresholds. As it can be seen, in these two metrics the 
proposed system (\emph{CGVS($ t_2 $)}) considers the central bias unlike the others. 
If the central bias were not considered, the results decrease but are still 
satisfactory (\emph{CGVS''}). However, in the remaining two metrics, the proposed 
system is the best, except in the PASCALS dataset where the best is the RF 
method (Fig. \ref{fig: metrics}).
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper1/metrics.png}
    \centering
    \caption{Metrics comparison.}
    \label{fig: metrics}
\end{figure}

\subsubsection{\emph{Between Saliency Map and Salient Object}}
Most fixation prediction methods perform poorly when used to detect salient 
objects. To solve this problem, a two-dimensional Gaussian distribution is 
applied to each salience map derived from any method. The derived output 
will be used as an initial CBSP from which the salient objects can be 
extracted with the previously proposed calculations.

\subsubsection{\emph{Extended Saliency-Related Applications}}
The peculiarity of the proposed method also lies in the search for salient 
edges. This process is possible by replacing the four color components with 
three luminance gradients and two color-opponent channels. The system also 
provide excellent text detection.

@@

\subsection{DISCUSSION}
The proposed model is able to search for different salient structures and the 
objects inside them, without using tools, such as the superpixel technique, 
adopted by other methods. The system can be extended by introducing 
other local features such as (e.g., depth, motion, etc.) to be used also 
in video processing. It is possible to carry out an analysis of the scene 
using unsupervised learning methods. Finally, this method offers a dual use. In 
a cluttered scene with no dominant objects, the system will function as a 
fixation prediction model. Finally, on the other hand, with simple scenes, 
the system detects existing relevant objects.
